### 2019-12-26 docs/thesis-project/article.tex
updt

Two parameters specify some of the most widely used coding algorithms, the number of data symbols \textit{k} to be encoded, and the number of coded symbols \textit{n} to be produced, both assumed to be in a finite field $GF(2^w)$ and these are referred as \textit{(n, k) erasure-codes}. The fundamental idea, is that a file of size $S$ is divided into $k$ equally sized fragments and encode them into $n$ encoded fragments, allowing the original file to recovered from any set of encoded-fragment with count $k$. Reed-Solomon codes are one such example. Systems that use these and other more sophisticated coding are evaluated under some of the following metrics, the \textbf{\textit{repair-bandwidth}}, i.e., the number of bits communicated in the network during normal and repair operations, the \textbf{\textit{disk I/O}} which is the number of bits read from disk during each repair, the \textbf{\textit{repair locality}} which is the number of peers that would be involved in the repair process; Since coding algorithms are slow processes CPU cycles, XOR operation counts and cache misses are metrics often researched as well \cite{fast_coding}, when the main interest is tied with load-balancing and cost savings. We take particular interest in the first metric because, in general, coding leads to bursts in bandwidth consumption. Whenever a peer fails, all files he held need to be quickly recovered by some peer who needs to gather enough fragments from possibly many different peers. Such burst in consumption may lead to delays or even failure of the repair process due to physical link capacity between peers, who are involved in the repair process, or even throughput constraints enforced by each peer.

>>>>

Two parameters specify some of the most widely used coding algorithms, the number of data symbols \textit{k} to be encoded, and the number of coded symbols \textit{n} to be produced, both assumed to be in a finite field $GF(2^w)$ and these are referred as \textit{(n, k) erasure-codes}. The fundamental idea, is that a file of size $S$ is divided into $k$ equally sized fragments and encode them into $n$ encoded fragments, allowing the original file to recovered from any set of encoded-fragment with count $k$. Systems that use these and other more sophisticated coding are evaluated under some of the following metrics, the \textbf{\textit{repair-bandwidth}}, i.e., the number of bits communicated in the network during normal and repair operations, the \textbf{\textit{disk I/O}} which is the number of bits read from disk during each repair, the \textbf{\textit{repair locality}} which is the number of peers that would be involved in the repair process; Since coding algorithms are slow processes CPU cycles, XOR operation counts and cache misses are metrics often researched as well \cite{fast_coding}, when the main interest is tied with load-balancing and cost savings. We take particular interest in the first metric because, in general, coding leads may lead to unreasonable bursts in bandwidth consumption when availability requirements, in very dynamic systems, are high \cite{coding-problems}, even for today's standards. Whenever a peer fails, all files he held need to be quickly recovered by some peer who needs to gather enough fragments from possibly many different peers. Such burst in consumption may lead to delays or even failure of the repair process due to physical link capacity between peers, who are involved in the repair process, or even throughput constraints enforced by each peer. When it comes to redundancy in a distributed storage systems, one fundamental question is deciding when to replicate or recover data; this is often called the replica-control problem.

There are two main approaches, reactive and proactive. Reactive approaches are the least complex, and consist of recovering data whenever a failure is detected; they suffer the most from bandwidth bursts, and mitigations to this problem include in using prediction models and thresholds to avoid unnecessary recoveries \cite{lifetime-reactive, efficient-replica-mng-reactive}. Proactive approaches seek to smooth bandwidth consumption by injecting new redundancy data into the network overtime at a fixed-rate \cite{proactive-rep, reliability-without-availability}. When it comes to coding techniques, the most widely known algorithms belong to the \textit{Maximum Distance Separable} (MDS) class, this class is likely to offer the best reliability-redundancy trade-off while consuming the least amount of storage space at the cost of increased repair-bandwidth, disk I/O and CPU time. Regardless of the chosen approach, research \cite{network-coding-for-dss} suggests that for coding to be competitive in distributed storage systems, one should seek to minimize these costs, while maximizing redundancy to only the amount necessary to ensure a specific service guarantee. They identify \textit{Minimum Bandwidth Regenerating} (MBS), and all codes in between these two ends of the spectrum as \textit{regenerating codes}, the differences between codes on the spectrum depend on the values such has \textit{n}, \textit{k} and on the implementation of the algorithms themselves. Shokrollahi \textit{et al.} introduces raptor codes \cite{raptor-codes}, which are a linear-time coding and decoding extension of LT codes \cite{lt-codes}. LT codes belong to the class of rateless codes, i.e., a potentially infinite sequence of encoded fragments can be generated from a given data source. Furthermore, the original data is recoverable from any subset of the encoded fragments of size equal to or slightly larger than original data size; These rateless code implementations are of particular importance because they are scalable with regards to the machine and network resources,  and fault-tolerant concerning dynamic and heterogeneous network environments. Finally, Zhou \textit{et al.} \cite{fast_coding} perform a study on state of the art techniques that improve coding efficiency through bitmatrix optimization, vectorization, and scheduling and prove that when used in conjunction much better levels of performance can be delivered, e.g., 552.27\% when compared to simple MDS implementations, in particular, the Reed-Solomon algorithm.
